\section{Proposed guidelines}\label{s:guidelines}

To assist in the establishment a minimum standard for the communication of computational results, it is proposed that the following could be inserted into the author and reviewer guidelines of journals in the weather and climate sciences. In places the language borrows from the guidelines recently adopted by \textit{Nature} \citep{Nature2014}. It is anticipated that a journal would also provide links to examples of well documented computational results to help both authors and reviewers in complying with these guidelines.

\subsection{Author guidelines}

If computer code is central to any of the paper's major conclusions, then the following is required as a minimum standard: 
\begin{enumerate}
\item A statement describing whether (and where) that code is available and setting out any restrictions on accessibility. Best practice involves managing code with a version control system such as Git, Subversion or Mercurial, which is then linked to a publicly accessible online repository such as GitHub or Bitbucket. Authors are not expected to produce a brand new repository to accompany their paper - an `everyday' repository which also contains code not relevant to the paper is fine.  
\item A high-level description of the software used to execute that code (including citations for any academic papers written to describe that software).
\item A supplementary file outlining the precise version of the software packages and operating system used. This information should be presented in the following format: name, version number, release date, institution and DOI or URL.
\item A supplementary log file for each major result (including key figures) showing all computational steps taken from the initial download/attainment of the data to the final result. Best practice includes the time/date each step was executed as well as the unique revision number (or hash value) indicating which version of the code repository was used. 
\end{enumerate}

Items 1 and 2 are often included in a `Computation Procedures' section with manuscript itself, while the supplementary files referred to in items 3 and 4 are often hosted on websites like Figshare or Zenodo.

Any practical issues preventing code sharing will be evaluated by the editors, who reserve the right to decline a paper if important code is unavailable. Authors should note that they are not obliged to support the reviewers or readers of this journal in repeating their computations.

\subsection{Reviewer guidelines}

The reviewer guidelines for most journals already ask if the methodology is explained in sufficient detail so that the paper's scientific conclusions could be tested by others. Such a statement could simply be added to as follows: "If computer code is central to any of those conclusions, then reviewers should ensure that the authors are compliant with the minimum standards outlined in the author guidelines. It should be noted that reviewers are not obliged to assess or execute the code associated with a submission. They must simply check that it is adequately documented."   
  